Playing Atari Breakout with Keras and R

### 2018-07-14 article/article.Rmd

![[Schematic illustration of the convolutional neural network. ](https://storage.googleapis.com/deepmind-media/dqn/DQNNaturePaper.pdf)](dqn.png)

@@

@@

>>>>

![[Schematic illustration of the convolutional neural network](https://storage.googleapis.com/deepmind-media/dqn/DQNNaturePaper.pdf)](dqn.png)

@@

![[Frame Stacking](https://web.stanford.edu/class/cs221/2017/restricted/p-final/vishakh/final.pdf)](stack.png)

@@

### Algorithm
<pre>
<b>Deep Q Learning with Experience Replay</b>

Initialize replay memory D to size N
Initialize action-value function Q with random weights
<b>for</b> episode = 1, M <b>do</b>
  Initialize state s<SUB>1</SUB>
  <b>for</b> t = 1, T <b>do</b>
    With probability λ select random action a<SUB>t</SUB>
    Otherwise select a<SUB>t</SUB> = argmax<SUB>a</SUB>Q(s<SUB>t</SUB>, a; θ<SUB>i</SUB>)
    Execute action a<SUB>t</SUB> in emulator and observe reward r<SUB>t</SUB> and image x<SUB>t+1</SUB>
    Set s<SUB>t+1</SUB> = {s<SUB>t</SUB>, a<SUB>t</SUB>, x<SUB>t+1</SUB>} and preprocess Φ<SUB>t+1</SUB> = Φ(s<SUB>t</SUB> + 1)
    Store transition (s<SUB>t</SUB>, a<SUB>t</SUB>, r<SUB>t</SUB>, s<SUB>t+1</SUB>) in D
      Set y<SUB>j</SUB>:= r<SUB>j</SUB> for terminal s<SUB>j+1</SUB>
      Set y<SUB>j</SUB>:= r<SUB>j</SUB> + γ max a<SUB>0</SUB>Q(Φ<SUB>j+1</SUB>, a<SUB>0</SUB>; θ) for non terminal φ<SUB>j+1</SUB>
    Sample a minibatch of transitions (s<SUB>j</SUB>, a<SUB>j</SUB>, r<SUB>j</SUB>, s<SUB>j+1</SUB>) from D
    Perform a gradient step on (y<SUB>j</SUB> − Q(s<SUB>j</SUB>, a<SUB>j</SUB>; θ<SUB>i</SUB>))<SUP>2</SUP> with respect to θ
  <b>return</b>
<b>return</b>

</pre>
